---
title: "MotorLearn_PosterPlots"
output: pdf_document
---


# load relevant data
```{r, include=FALSE, echo=FALSE}
source('IGAS_ProcessFunctions.R')

#rm(list=ls())
###### data loading and organization #######

# load the processed data from experiment 1 and 2
e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')

options(contrasts = c("contr.sum", "contr.poly"))
defaultContrasts = options()$contrasts
theme_set(theme_classic())

dodge <- position_dodge(width = 0.9)
e2GrpPos <- c("400","500","625","675","800","900")
e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")

e1Pos <- c("610","760","835","910")
e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
```

## Experiment 1 

# Training - Experiment 1
```{r}

exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter))

exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>% group_by(Group,sbjCode) %>%
  group_by(sbjCode,Group,conditType,trainHalf) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter))

exp1TrainPosition %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
  geom_bar(aes(group=trainHalf,fill=trainHalf),stat="summary",fun=mean,position=dodge)+
  facet_wrap(~conditType,ncol=2)+
  stat_summary(aes(x=positionX,group=trainHalf),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
  ylab("Mean Distance From Center Of Target")+
  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)


model<-ezANOVA(exp1Train,dv=MeanTargetDistance,within=c(trainHalf),between=Group,wid=sbjCode,type=3);show(model)

aggregate(MeanTargetDistance ~ conditType + positionX,data=exp1TrainPosition,mean)

                            
```


#Experiment 1 Testing Phase
```{r}

exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% 
  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()

exp1.Test2 <- exp1.Test %>% group_by(sbjCode,conditType) %>% 
  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaleDev = mean(MeanScaleDev),.groups="keep")%>% as.data.frame()

#manuscript plot
exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)

m1 <- exp1.Test %>% anova_test(dv=MeanTargetDeviance,between=conditType,within=positionX,wid=sbjCode,type=3); show(m1)



cnames=c("Condition","610","760","835","910","")
test= exp1.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>% 
  summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2)) 
test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(Condition,positionX,msd,gsd)%>%pivot_wider(names_from = positionX,values_from=c(msd,gsd))
test=test[,1:6] %>% as.data.frame()
colnames(test) <- cnames
stargazer(test,type="text",summary=FALSE,rownames=FALSE)


```

# Experiment 1 Identity Contrast (760) and novel position contrast (835)
```{r}
exp1.Test %>% filter(ThrowPosition=="Constant Location") %>% anova_test(dv=MeanTargetDeviance,between=conditType,wid=sbjCode,type=3)
exp1.Test %>% filter(ThrowPosition=="Novel Location") %>% anova_test(dv=MeanTargetDeviance,between=conditType,wid=sbjCode,type=3)
```







### Experiment 2 ###



# Experiment 2 - calculate various distances between transfer throw position and training throw position
```{r,echo=FALSE}

exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()

exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()

transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()

transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% convert_as_factor(testHalf)

variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))

transfer <- rbind(variedTest,constantTest)
transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% convert_as_factor(novel,extrapolate)

transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()


# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
# novelAll <- novelAll %>% group_by(positionX) %>%
#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()

novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)


constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
variedTest <- transfer %>% filter(condit==7) # only varied testing
variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity


variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant

exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()

exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()

exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()

exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()

exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()

```


# Training - Experiment 2
```{r}

exp2TrainPosition %>% ggplot(aes(x=trainHalf,y=MeanTargetDistance))+
  geom_bar(aes(group=trainHalf,fill=trainHalf),stat="summary",position=dodge,fun="mean")+
  stat_summary(aes(x=trainHalf,group=trainHalf),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)

exp2TrainPosition %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
  geom_bar(aes(group=trainHalf,fill=trainHalf),stat="summary",position=dodge,fun="mean")+
  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=trainHalf),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)

model<-ezANOVA(exp2Train,dv=MeanTargetDistance,within=c(trainHalf),between=conditType,wid=sbjCode,type=3);show(model)

model<-exp2Train %>% anova_test(dv=MeanTargetDistance,within=trainHalf,between=conditType,wid=sbjCode,type=3);show(model)


t<- e2  %>% filter(stage!="Transfer") %>%ungroup()  %>% rename(Condition="conditType") %>% group_by(Condition,ThrowPosition) %>% 
  summarise(Mean=round(mean(AbsDistFromCenter),2),sd=round(sd(AbsDistFromCenter),2),msd=paste(Mean,"(",sd,")",sep=""),.groups="keep") %>%
   select(-Mean,-sd) %>% spread(ThrowPosition,msd) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)
t<- e2  %>% filter(stage!="Transfer") %>%ungroup()  %>% rename(Condition="conditType") %>% group_by(Group,ThrowPosition) %>% 
  summarise(Mean=round(mean(AbsDistFromCenter),2),sd=round(sd(AbsDistFromCenter),2),msd=paste(Mean,"(",sd,")",sep=""),.groups="keep") %>%
   select(-Mean,-sd) %>% spread(ThrowPosition,msd) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)

```






#Experiment 2 - Testing Phase - General Comparison
```{r,fig.height=6,fig.width=7}
# manuscript plot
exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun.y="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)

# manuscript analysis
mg2=exp2.Test2 %>% anova_test(dv=MeanScaledDev,between=conditType,wid=sbjCode,type=3);show(mg2) 

cnames=c("Condition","400","500","625","675","800","900","")
test= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,ThrowPosition) %>% 
  summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2)) 
test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(Condition,ThrowPosition,msd,gsd)%>%pivot_wider(names_from = ThrowPosition,values_from=c(msd,gsd))
test=test[,1:8] %>% as.data.frame()
colnames(test) <- cnames
stargazer(test,type="text",summary=FALSE,rownames=FALSE)

```



# Experiment 2 - Testing Showing all 7 Groups
```{r}

exp2.Test7 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=Group2,fill=Group2))+geom_bar(stat="summary",position=position_dodge(),fun.y="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Position"))+theme(legend.title.align=.25)

exp2.Test7 %>% 
  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
  facet_wrap(~ThrowPosition4)+
  ylab("Mean Distance From Center Of Target")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Training Condition"))+
  theme(legend.title.align=.25)+
  scale_x_discrete(name=" Training Group",labels=e2Labels)

exp2.Test7.agg %>% ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +
  theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Training Group",labels=e2Labels)


```




# Experiment 2  - only novel positions
```{r}
sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()

sum.novelAll2 <- sum.novelAll %>% group_by(sbjCode,conditType) %>% 
  summarise(MeanTargetDev=mean(MeanTargetDev),MeanScaledDev=mean(MeanScaledDev),.groups="keep") %>% as.data.frame()

mn2=sum.novelAll2 %>% anova_test(dv=MeanScaledDev,between=conditType,wid=sbjCode,type=3);show(mn2)




cnames=c("Condition","400","500","625","675","800","900","")
test=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>% 
  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2)) 
test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(Condition,positionX,msd,gsd)%>%pivot_wider(names_from = positionX,values_from=c(msd,gsd))
test=test[,1:8] %>% as.data.frame()
colnames(test) <- cnames
stargazer(test,type="text",summary=FALSE,rownames=FALSE)


##################


```





# Experiment 2 - Testing Stage - Varied vs. Constant identity - trained position for constant, novel for varied
```{r}
sum.variedVsNovelIden <- variedVsNovelIden  %>%
  group_by(sbjCode,conditType,positionX) %>% 
  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()

sum.variedVsNovelIden2 <- sum.variedVsNovelIden %>%
  group_by(sbjCode,conditType) %>% 
  summarise(MeanTargetDev=mean(MeanTargetDev,trim=.05),MeanScaledDev=mean(MeanScaledDev))%>% as.data.frame()

# manuscript analysis
mi4=sum.variedVsNovelIden2 %>% anova_test(dv=MeanScaledDev,between=conditType,wid=sbjCode,type=3);show(mi4)


cnames=c("Condition","400","625","675","900","")
test=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>% 
  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2)) 
test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(Condition,positionX,msd,gsd)%>%pivot_wider(names_from = positionX,values_from=c(msd,gsd))
test=test[,1:6] %>% as.data.frame()
colnames(test) <- cnames
stargazer(test,type="text",summary=FALSE,rownames=FALSE)


# manuscript plot
sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun.y="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
 
```





### re-doing experiment 2 comparisons while controlling for similarity (1c) ###


# effect of similarity
```{r}
dSim <- readRDS("data/IGAS_Similarity-Performance.rds") %>% rename(positionX=pos)
transferSim <- merge(exp2.Test,dSim,by=c("sbjCode","conditType","positionX")) %>% as.data.frame()
transferSim2 <- transferSim %>% ungroup() %>% 
  group_by(sbjCode,conditType) %>% summarise(MeanTargetDeviance=mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev),sim_c=mean(sim_c)) %>% ungroup() %>% as.data.frame()

lm.sim=dSim %>% lm(dev ~ sim_c, data=.);summary(lm.sim)

```


# general comparison - with similarity
```{r}


m6=transferSim2 %>% anova_test(dv=MeanScaledDev,between=conditType,covariate=sim_c,wid=sbjCode,type=3);show(m6)


```


## varied vs constant identity - (not 500 or 800) - while controlling for sim ##
```{r}

sum.variedVsNovelIden <- variedVsNovelIden %>% 
  group_by(sbjCode,conditType,positionX) %>% 
  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) 

idenSimPos <- merge(sum.variedVsNovelIden,dSim,by=c("sbjCode","conditType","positionX")) %>% group_by(sbjCode,conditType,positionX) %>%summarise(MeanTargetDev=mean(MeanTargetDev),MeanScaledDev=mean(MeanScaledDev),sim_c=mean(sim_c),sim_cvcc=mean(sim_cvcc)) %>%ungroup() %>% as.data.frame()

idenSim <- idenSimPos %>% group_by(sbjCode,conditType) %>%
  summarise(MeanTargetDev=mean(MeanTargetDev),MeanScaledDev=mean(MeanScaledDev),sim_c=mean(sim_c),sim_cvcc=mean(sim_cvcc)) %>%ungroup() %>% as.data.frame()

m8 <- idenSim %>% anova_test(dv=MeanScaledDev,between=conditType,wid=sbjCode,covariate = sim_c,type=3);show(m8)


```








# plots of task and solution space
```{r}

library("RColorBrewer")

taskspace <- e2 %>% filter(AbsDistFromCenter<900)
taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
taskspace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=trialType2),alpha=0.5) + ggtitle(" Experiment 2. Example of full task space - Position 900")


taskspace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=hitOrMiss),alpha=0.5) 


solSpace <- e2 %>% filter(trialType==11)
#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("") 

solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)


missSpace <- e2 %>% filter(trialType !=11)
missSpace$Result = "Missed Target"
solSpace$Result <- solSpace$Result

# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 

# multiplied velocoties by -1 to make the axes less confusing
solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + geom_point(aes(colour=Result),alpha=0.6) + scale_color_manual(values =brewer.pal(n=6,name="Set1"))+labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")


fullSpace <- rbind(missSpace,solSpace)

fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") 








```








